---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# golem.test

<!-- badges: start -->
<!-- badges: end -->

Testing the deployment of a [golem](https://thinkr-open.github.io/golem/) app on [Heroku](https://www.heroku.com/)

## Installation

You can install the development version of golem.test from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("bkm-consultants/golem-test")
```

In case you are using `renv`

```{r eval=FALSE}
# install.packages("renv")
# renv::activate()
renv::install("bkm-consultants/golem-test")
```

## [Dev] Building Docker image and running the container locally

### Prerequisites

#### Linux (Ubuntu)

[Docker Engine](https://docs.docker.com/engine/install/ubuntu/)

Alternative: [Docker Desktop](https://docs.docker.com/desktop/linux/install/)

#### macOS

[Docker Desktop](https://docs.docker.com/desktop/mac/install/)    

#### Windows

1. [Windows Subsystem for Linux (WSL/WSL2)](https://docs.microsoft.com/en-us/windows/wsl/install)
1. [Docker Desktop](https://docs.docker.com/desktop/windows/install/)
    
Build Docker image

```{bash, eval=FALSE}
docker build -t golem-test .
```

Run container

```{bash, eval=FALSE}
docker run -d --rm --name golem-test -e PORT=5000 -p 5001:5000 golem-test
```

Open browser

```{bash, eval=FALSE}
# Linux/Windows via WSL
xdg-open http://localhost:5001 

# macOS
open http://localhost:5001
```

## [Staging]

TBD

## [Prod] Deployment on [Heroku](heroku.com/)

If it doesn't exist yet create a `heroku.yml` file in your application’s root directory. 

```
build:
  docker:
    web: Dockerfile
```

Set stack of the app to `container`

```{bash eval=FALSE}
heroku stack:set container -a golem-test
```

Push app to Heroku

```{bash eval=FALSE}
git push origin main
```

